### 2022-01-28 chapter5/chapter.tex
same draft

%!TEX root = ../thesis.tex
\chapter{Global convergence results}\label{ch: global results}
In this chapter we prove a number of results which stem from the main results of Chapter~\ref{sec: conv}. We consider the discrete-time embedded processes formed by observing the QBD-RAP at the orbit restart epochs and by observing the fluid queue at the hitting times of the level process at the of points \(\{y_\ell\}\), which are the boundaries of the intervals \(\{\calD_\ell\}\). In Corollary~\ref{cor: aln22222212} we prove that the transition probability of the embedded process of the QBD-RAP converge those of the embedded process of the fluid queue. In Corollary~\ref{cor: short cor} we prove that distribution of the sojourn time of the QBD-RAP in a given level converges to distribution of the sojourn time of the fluid queue in the corresponding interval. In Section~\ref{sec: sub global}, we state global results on the weak convergence (in space and time) of the QBD-RAP approximation scheme to the fluid queue.

@@

\section{Convergence of the QBD-RAP scheme}\label{sec: local to global}
The rest of this chapter is dedicated to proving a global convergence results of the QBD-RAP approximation scheme to the fluid queue. Ultimately, we prove the weak convergence (in space and time) of the QBD-RAP approximation scheme to the distribution of the fluid queue. The structure of the argument is to first show a convergence result for the Laplace transform with respect to time of the distributions of the QBD-RAP and fluid queue at the \(n\)th orbit restart epoch. We then prove a convergence result of the QBD-RAP and fluid queue between the \(n\)th and \(n+1\)th orbit restart epoch. Summing over the number of orbit restart epochs, \(n\), and via the Dominated Convergence Theorem, we claim a convergence of the Laplace transforms with respect to time of the QBD-RAP approximation and fluid queue. Lastly, we apply the Extended Continuity Theorem for Laplace transforms \cite[Chapter XIII, Theorem 2a]{feller1957} to claim a weak convergence (in space and time) of the QBD-RAP approximation scheme to the fluid queue.

@@

Let 
\begin{align}\label{eqn: paths set1}
	\mathcal P^n_{\ell_0,\ell_n}&=\left\{(\ell_1,\dots,\ell_{n-1}) \in \mathcal K^{n-1}\Bigg| \begin{array}{c}  \ell_{r-1}=\ell_r=0 \mbox{ or } \ell_{r-1}=\ell_r=K
		\\ \mbox{ or }|\ell_{r-1}-\ell_r|=1,r = 1,\dots,n\end{array}\right\}.
\end{align}
The set \(\mathcal P^n_{\ell_0,\ell}\) contains all the possible values which \(\{L(\tau_m)\}_{m=2}^{n-1}\) may take on a sample path which starts in level \(\ell_0\), ends in level \(\ell\) and has \(n\) orbit restart epochs. Similarly, \(\mathcal P^n_{\ell_0,\ell}\) contains all the possible values which \(\{X(\tau_m^X)\}_{m=2}^{n-1}\) may take on a sample path which starts in band \(\ell_0\), ends in band \(\ell\) at time \(\tau_n^X\).

Thus, by partitioning on the times \(\tau_m\), \(m=2,\dots,n-1\), and the phases and the levels at these times and using the strong Markov property of the QBD-RAP, then (\ref{eqn: dskvnaSF}) is  
	\begin{align}
		\sum_{\substack{j_2,\dots,j_{n-1}\in\mathcal S \\ (\ell_2,\dots,\ell_{n-1}) \in\mathcal P^{n-1}_{\ell_1,\ell}}}\prod_{m=2}^{n}&\mathbb P(\Ydp(m) =(\ell_m, j_m), 
		\tau_{m}^{(p)}\leq E^\lambda 
		\mid  \nonumber 
\Ydp (m-1) = (\ell_{m-1}, j_{m-1}), \\&\tau_{m-1}^{(p)}\leq E^\lambda ) \nonumber
		%
		\\=\sum_{\substack{j_2,\dots,j_{n-1}\in\mathcal S \\ (\ell_2,\dots,\ell_{n-1}) \in\mathcal P^{n-1}_{\ell_1,\ell}}}\prod_{m=2}^{n}&\mathbb P(\Ydp(1) =(\ell_m, j_m), \tau_{1}^{(p)}\leq E^\lambda 
            	 \mid  
	 	\bs Y^{(p)}(0) = (\ell_{m-1},\bs \alpha, j_{m-1})),  \label{eqn: 161222}
\end{align}
by the time-homogeneity property of the QBD-RAP and the memoryless property of \(E^\lambda\) and where we define \(\ell_n=\ell\) for notational convenience. %Each factor in the product is 
% \begin{align}
% 	&\mathbb P(\Ydp(m) = (\ell_m, j_m), \tau_{m}^{(p)}\leq E^\lambda 
%             	 \mid \Ydp(m-1) = (\ell_{m-1}, \nonumber
% 	 	 j_{m-1}), \tau_{m-1}^{(p)}\leq E^\lambda) 
% 	\\&=\mathbb P(\Ydp(m) = (\ell_m, j_m), \tau_{m}^{(p)}\leq E^\lambda 
%             	 \mid \Ydp(0) = (\ell_{m-1}, j_{m-1}), \tau_{m-1^{(p)}}=0)\nonumber
% 	\\&=\mathbb P(\Ydp(1) = (\ell_m, j_m), \tau_{1}^{(p)}\leq E^\lambda 
%             	 \mid \Ydp(0) = (\ell_{m-1}, j_{m-1}))\label{eqn: kk}
% \end{align}
% by the time-homogeneous property of the QBD-RAP and the memoryless property of the exponential distribution. 
We can apply Corollary (\ref{cor: aln222}) to the factors of the summands in (\ref{eqn: 161222}) and conclude 
\begin{align}
	& \mathbb P(\Ydp(1) = (\ell_m, j_m), \tau_{1}^{(p)}\leq E^\lambda 
            	 \mid \bs Y^{(p)}(0) = (\ell_{m-1},\bs \alpha, j_{m-1}))\nonumber
	%
	\\&\to \mathbb P(\bs X(\tau_1^X) =( y_{\ell_{m}+1(j_m\in\calS_-)},j_m), \tau_{1}^X\leq E^\lambda 
	\mid \bs X(0) = (y_{\ell_{m-1}+1(j_{m-1}\in\calS_-)}, j_{m-1}))  \label{eqn:kknvf fawoprgj v2}
\end{align}

By the time-homogeneous property of the fluid queue and the memoryless property of the exponential distribution, (\ref{eqn:kknvf fawoprgj v2}) is equal to 
\begin{align}
	\mathbb P(\bs X(\tau_m^X) =( y_{\ell_{m}+1(j_m\in\calS_-)},j_m), \tau_{m}^X\leq E^\lambda 
		\mid \bs X(\tau_{m-1}) = (y_{\ell_{m-1}+1(j_{m-1}\in\calS_-)}, j_{m-1})).\label{eqn: lim 12}
\end{align}
% \begin{align}
% 	&\mathbb P(\bs X(\tau_1^X) = (y_{\ell_{m-1}+1}, j_m), \tau_{1}^X\leq E^\lambda 
%             	 \mid \bs X(0) = (x_0, j_{m-1})) \nonumber
% 	%  \\&=\mathbb P(\bs X(\tau_m^X) = (y_{\ell_{m-1}+1}, j_m), \tau_{m}^X\leq E^\lambda 
%     %         	 \mid \bs X(\tau_{m-1}^X) = (x_0, j_{m-1}))\nonumber 
% 	 \\&=\mathbb P(\bs X(\tau_m^X) = (y_{\ell_{m-1}+1}, j_m), \tau_{m}^X\leq E^\lambda 
%             	 \mid \bs X(\tau_{m-1}^X) = (x_0, j_{m-1}), \nonumber 
% 	\tau_{m-1}^X\leq E^{\lambda}).
% \end{align}
% Similarly, 
% \begin{align}
% 	&\mathbb P(\bs X(\tau_1^X) = (y_{\ell_{m-1}}, j_m), \tau_{1}^X\leq E^\lambda 
%             	 \mid \bs X(0) = (x_0, j_{m-1})) \nonumber
% 	 \\&=\mathbb P(\bs X(\tau_m^X) = (y_{\ell_{m-1}}, j_m), \tau_{m}^X\leq E^\lambda 
%             	 \mid \bs X(\tau_{m-1}^X) = (x_0, j_{m-1}), \tau_{m-1}^X\leq E^\lambda).
% \end{align}

Thus, returning to (\ref{eqn: 161222}) and taking the limit as \(p\to\infty\),  
\begin{align}
	&\lim_{p\to\infty}\sum_{\substack{j_2,\dots,j_{n-1}\in\mathcal S \\ (\ell_2,\dots,\ell_{n-1}) \in\mathcal P^{n-1}_{\ell_1,\ell}}}\prod_{m=2}^{n}\mathbb P(\Ydp(1) = (\ell_m, j_m), \tau_{1}^{(p)}\leq E^\lambda \nonumber
            	 \mid \bs Y^{(p)}(0) = (\ell_{m-1},\bs\alpha, j_{m-1})) \nonumber 
	%
	\\ &=\sum_{\substack{j_2,\dots,j_{n-1}\in\mathcal S \\ (\ell_2,\dots,\ell_{n-1}) \in\mathcal P^{n-1}_{\ell_1,\ell}}}\prod_{m=2}^{n}\lim_{p\to\infty} \mathbb P(\Ydp(1) = (\ell_m, j_m), \tau_{1}^{(p)}\leq E^\lambda \nonumber
            	 \mid \bs Y^{(p)}(0) = (\ell_{m-1}, \bs\alpha,
	 	 j_{m-1}) ),
	 \label{eqn: 161222b}
\end{align}
where we may swap the limit and the sums as they are finite, and we can swap the limit and the product since all the limits exist and the product is finite. Substituting the limits (\ref{eqn: lim 12}) into (\ref{eqn: 161222b}) gives 
\begin{align}
	&\sum_{\substack{j_2,\dots,j_{n-1}\in\mathcal S \\ (\ell_2,\dots,\ell_{n-1}) \in\mathcal P^{n-1}_{\ell_1,\ell}}} \prod_{m=2}^{n}\mathbb P(\bs X(\tau_m^X) = (y_{\ell_{m}+1(j_{m}\in\mathcal S_-)}, j_m), \tau_{m}^X\leq E^\lambda\mid \nonumber
            	\\&\qquad\qquad  \bs X(\tau_{m-1}^X)=(y_{\ell_{m-1}+1(j_{m-1}\in\mathcal S_-)},j_{m-1}),\tau_{m-1}^X\leq E^\lambda),\nonumber
		%
		\\&= \mathbb P(\bs X(\tau_n^X) = (y_{\ell+1(j_{n}\in\mathcal S_-)}, 
		j_n), \tau_{n}^X\leq E^\lambda \mid \bs X(0)=(y_{\ell_{1}+1(j_{1}\in\mathcal S_-)},
		j_{1}), 
		\tau_1^X\leq E^\lambda),
\end{align}
by the strong Markov property of the fluid queue and the Law of total probability.

@@

\subsection{Between the \(n\)th and \(n+1\)th orbit restart epochs}\label{sec: between n and np1}
Let \(\mathcal T_n^{(p)} = (\tau_{n}^{(p)},\tau_{n+1}^{(p)}]\) and \(\mathcal T_n^X=(\tau_n^X,\tau_{n+1}^X]\). Consider the Laplace transform 
\begin{align}
	\nonumber&\int_{t=0}^\infty e^{-\lambda t}\int_{x\in\calD_{\ell,j}}\mathbb P({\bs Y}^{(p)}(t) = (\ell, \wrt x, j), t\in\mathcal T_n^{(p)} \mid 
	\bs Y^{(p)}(0)=\bs y_0^{(p)})\psi(x)\wrt t,
	% \nonumber&\int_{t=0}^\infty e^{-\lambda t}\int_{x\in\calD_\ell}\mathbb P(L^{(p)}(t) = \ell, \widetilde X^{(p)}(t)\in\wrt x, \phi^{(p)}(t) = j, \tau_{n}^{(p)}\leq t<\tau_{n+1}^{(p)} \mid L^{(p)}(0)=\ell_0, 
	% 	\\&\qquad \bs A^{(p)}(0)=\bs a_{\ell_0,i}^{(p)}(x_0), \phi^{(p)}(0)=i)\psi(x)\wrt t.
\end{align}
where \(\psi:\mathbb R\to \mathbb R\) is a bounded function.

Partitioning on the time of the \(n\)th orbit restart epoch and the phase and level at this time gives
\begin{align}
	&\int_{t=0}^\infty e^{-\lambda t} 
	\int_{x\in\calD_{\ell,j}}
	\int_{u_n=0}^t\sum_{j_n\in\mathcal S} \mathbb P({\bs Y}^{(p)}(t) = (\ell,\wrt x,j), 
	t \in(u_n, \tau_{n+1}^{(p)}] \mid\Ydp(n) = (\ell,j_n), \nonumber 
	\\&\quad \tau_{n}^{(p)}= u_n)\psi(x) \mathbb P(\Ydp(n) = (\ell, j_n), \tau_{n}^{(p)}\in \wrt u_n 
	 \mid \bs Y^{(p)}(0)=\bs y_0^{(p)}) 
	  \wrt t \nonumber 
	 %
	 \\&= \sum_{j_n\in\mathcal S}
	\int_{x\in\calD_{\ell,j}} \int_{t=0}^\infty e^{-\lambda t} \mathbb P({\bs Y}^{(p)}(t) = (\ell,\wrt x, j), 
	t\in\mathcal T_{0}^{(p)} \mid\nonumber 
	  \bs Y(0) = (\ell,\bs\alpha,j_n))\wrt t \psi(x)  
	  \\&\quad{} \mathbb P(\Ydp(n) = (\ell,j_n), \tau_{n}^{(p)}\leq E^\lambda 
	 \mid \bs Y^{(p)}(0)=\bs y_0^{(p)}) \label{eqn: l whkrqvlkjbrd}
\end{align}
by the time homogenous property of the QBD-RAP, the memoryless property of the exponential distribution, and the convolution theorem of Laplace transforms. The swap of integrals and sums is justified by the Fubini-Tonelli Theorem. We recognise the probability 
\begin{align}
	\mathbb P(\Ydp(n) = (\ell, j_n), \tau_{n}^{(p)}\leq E^\lambda 
	 \mid \bs Y^{(p)}(0)=\bs y_0^{(p)}) \label{eqn: Kkk nj aa w}
\end{align}
as that appearing in Lemma \ref{lem: kKKJJJF}, hence (\ref{eqn: Kkk nj aa w}) converges to 
\begin{align}
	\mathbb P(\bs X(\tau_n^X) = (y_{\ell+1(j_{n}\in\mathcal S_-)}, 
		j_n), \tau_{n}^X\leq E^\lambda
		\mid \bs X(0)=(x_0, i)) \label{eqn: ashverkjbvjhkhdsknacva}
\end{align}
as \(p\to\infty\).

Now consider the expression 
\begin{align}
	&\int_{x\in\calD_{\ell,j}} \int_{t=0}^\infty e^{-\lambda t} \mathbb P({\bs Y}^{(p)}(t) = (\ell,\wrt x, j),  
	t\in\mathcal T_0^{(p)} \mid \bs Y(0) = (\ell,\bs\alpha, j_n)
	 	 )\wrt t  \psi(x)  \label{eqn: vajkl;vJK:GSKJ}
\end{align}
which appears as part of (\ref{eqn: l whkrqvlkjbrd}). We can rewrite (\ref{eqn: vajkl;vJK:GSKJ}) as  
\begin{align}
	 &\int_{x\in\calD_{\ell,j}} \int_{t=0}^\infty e^{-\lambda t} \mathbb P({\bs Y}^{(p)}(t) = (\ell,\wrt x,j), 
	t\in\mathcal T_0^{(p)}\mid \Ydp(0) = (\ell,j_n))\wrt t \psi(x) \nonumber 
	 \\&= \int_{x\in\calD_{\ell,j}} \widehat f^{\ell,(p)} (\lambda)(x,j;y_{\ell+1(j_n\in\mathcal S_-)},j_n) \psi(x)\wrt x \label{eqn: Jk jJ KK}
\end{align}
Applying Theorem~\ref{thm: a thm!}, then (\ref{eqn: Jk jJ KK}) converges to 
\begin{align}
	&\int_{x\in\calD_{\ell,j}} \widehat \mu^{\ell} (\lambda)(x,j;y_{\ell+1(j_n\in\mathcal S_-)},j_n) \psi(x)\wrt x \nonumber 
	\\&= \int_{x\in\calD_{\ell,j}} \int_{t=0}^\infty e^{-\lambda t}\mathbb P(\bs X(t)\in(\wrt x, j), t\in\mathcal T_0^X \mid \bs X(0) = (y_{\ell+1(j_n\in\mathcal S_-)}, j_n) ) \psi(x). \label{eqn: lkHAHJFHKJ J J H}
\end{align}
Since the fluid queue is time-homogeneous and \(E^\lambda\) memoryless, then (\ref{eqn: lkHAHJFHKJ J J H}) is equal to 
\begin{align}
	&\int_{x\in\calD_{\ell,j}} \int_{t=0}^\infty e^{-\lambda t} \mathbb P(\bs X(t)\in(\wrt x,j), t\in\mathcal T_n^{X} \mid  
	\bs X(\tau_n^X) = (y_{\ell+1(j_n\in\mathcal S_-)},j_n), \tau_n^X\leq E^\lambda ) \psi(x)  \label{eqn: lkHAHJFHKJ J J 22}
\end{align}
Therefore, we have shown (\ref{eqn: vajkl;vJK:GSKJ}) converges to (\ref{eqn: lkHAHJFHKJ J J 22}) as \(p\to\infty\).

>>>>

%!TEX root = ../thesis.tex
\chapter{Global convergence results}\label{ch: global results}
In this chapter we prove some results which stem from the main results of Chapter~\ref{sec: conv}. We consider the discrete-time embedded processes formed by observing the QBD-RAP at the orbit restart epochs and by observing the fluid queue at the hitting times of the level process at the of points \(\{y_\ell\}\), which are the boundaries of the intervals \(\{\calD_\ell\}\). In Corollary~\ref{cor: aln22222212} we prove that the transition probability of the embedded process of the QBD-RAP converge those of the embedded process of the fluid queue. In Corollary~\ref{cor: short cor} we prove that distribution of the sojourn time of the QBD-RAP in a given level converges to distribution of the sojourn time of the fluid queue in the corresponding interval. In Section~\ref{sec: sub global}, we state global results on the weak convergence (in space and time) of the QBD-RAP approximation scheme to the fluid queue.

In this chapter we work with the augmented state space scheme to model phases with rates \(c_i=0\) as described in Section~\ref{sec: zero states}. The results of this chapter rely on results of Chapter~\ref{sec: conv} and therefore apply to the QBD-RAP scheme which uses ephemeral states to model a fluid queue which starts in a phase with rate \(0\), as described in Section~\ref{sec: initial conditions}. However, supplementing the results of Chapter~\ref{sec: conv} with the results from Appendix~\ref{app:extend conv} and using the same arguments from this chapter with only slight modifications, then the results of this chapter can be extended to the augmented state-space QBD-RAP scheme without the initial ephemeral phases.

@@

\section{Convergence of the QBD-RAP scheme}\label{sec: local to global}
This section is dedicated to proving a global convergence results of the QBD-RAP approximation scheme to the fluid queue. Ultimately, we prove the weak convergence (in space and time) of the QBD-RAP approximation scheme to the distribution of the fluid queue. The structure of the argument is to first show a convergence result for the Laplace transform with respect to time of the distributions of the QBD-RAP and fluid queue at the \(n\)th orbit restart epoch. We then prove a convergence result of the QBD-RAP and fluid queue between the \(n\)th and \(n+1\)th orbit restart epoch. Summing over the number of orbit restart epochs, \(n\), and via the Dominated Convergence Theorem, we claim a convergence of the Laplace transforms with respect to time of the QBD-RAP approximation and fluid queue. Lastly, we apply the Extended Continuity Theorem for Laplace transforms \cite[Chapter XIII, Theorem 2a]{feller1957} to claim a weak convergence (in space and time) of the QBD-RAP approximation scheme to the fluid queue.

@@

Let 
\begin{align}\label{eqn: paths set1}
	\mathcal P^n_{\ell_0,\ell_n}&=\left\{(\ell_1,\dots,\ell_{n-1}) \in \mathcal K^{n-1}\Bigg| \begin{array}{c}  \ell_{r-1}=\ell_r=0 \mbox{ or } \ell_{r-1}=\ell_r=K
		\\ \mbox{ or }|\ell_{r-1}-\ell_r|=1,r = 1,\dots,n\end{array}\right\}.
\end{align}
The set \(\mathcal P^n_{\ell_0,\ell}\) contains all the possible values which \(\{L(\tau_m)\}_{m=2}^{n-1}\) may take on a sample path which starts in level \(\ell_0\), ends in level \(\ell\) and has \(n\) orbit restart epochs. %Similarly, \(\mathcal P^n_{\ell_0,\ell}\) contains all the possible values which \(\{X(\tau_m^X)\}_{m=2}^{n-1}\) may take on a sample path which starts in band \(\ell_0\), ends in band \(\ell\) at time \(\tau_n^X\).

Thus, by partitioning on the phases and the levels at the times \(\tau_m\), \(m=2,\dots,n-1\),and using the strong Markov property of the QBD-RAP, then (\ref{eqn: dskvnaSF}) is  
	\begin{align}
		\sum_{\substack{j_2,\dots,j_{n-1}\in\mathcal S \\ (\ell_2,\dots,\ell_{n-1}) \in\mathcal P^{n-1}_{\ell_1,\ell}}}\prod_{m=2}^{n}&\mathbb P(\Ydp(m) =(\ell_m, j_m), 
		\tau_{m}^{(p)}\leq E^\lambda 
		\mid  \nonumber 
\Ydp (m-1) = (\ell_{m-1}, j_{m-1}), \\&\tau_{m-1}^{(p)}\leq E^\lambda ) \nonumber
		%
		\\=\sum_{\substack{j_2,\dots,j_{n-1}\in\mathcal S \\ (\ell_2,\dots,\ell_{n-1}) \in\mathcal P^{n-1}_{\ell_1,\ell}}}\prod_{m=2}^{n}&\mathbb P(\Ydp(1) =(\ell_m, j_m), \tau_{1}^{(p)}\leq E^\lambda 
            	 \mid  
	 	\bs Y^{(p)}(0) = (\ell_{m-1},\bs \alpha, j_{m-1})),  \label{eqn: 161222}
\end{align}
by the time-homogeneity property of the QBD-RAP and the memoryless property of \(E^\lambda\) and where we define \(\ell_n=\ell\) for notational convenience. %Each factor in the product is 
% \begin{align}
% 	&\mathbb P(\Ydp(m) = (\ell_m, j_m), \tau_{m}^{(p)}\leq E^\lambda 
%             	 \mid \Ydp(m-1) = (\ell_{m-1}, \nonumber
% 	 	 j_{m-1}), \tau_{m-1}^{(p)}\leq E^\lambda) 
% 	\\&=\mathbb P(\Ydp(m) = (\ell_m, j_m), \tau_{m}^{(p)}\leq E^\lambda 
%             	 \mid \Ydp(0) = (\ell_{m-1}, j_{m-1}), \tau_{m-1^{(p)}}=0)\nonumber
% 	\\&=\mathbb P(\Ydp(1) = (\ell_m, j_m), \tau_{1}^{(p)}\leq E^\lambda 
%             	 \mid \Ydp(0) = (\ell_{m-1}, j_{m-1}))\label{eqn: kk}
% \end{align}
% by the time-homogeneous property of the QBD-RAP and the memoryless property of the exponential distribution. 
We can apply Corollary \ref{cor: aln222} to the factors of the summands in (\ref{eqn: 161222}) and conclude 
\begin{align}
	& \mathbb P(\Ydp(1) = (\ell_m, j_m), \tau_{1}^{(p)}\leq E^\lambda 
            	 \mid \bs Y^{(p)}(0) = (\ell_{m-1},\bs \alpha, j_{m-1}))\nonumber
	%
	\\&\to \mathbb P(\bs X(\tau_1^X) =( y_{\ell_{m}+1(j_m\in\calS_-)},j_m), \tau_{1}^X\leq E^\lambda 
	\mid \bs X(0) = (y_{\ell_{m-1}+1(j_{m-1}\in\calS_-)}, j_{m-1})).  \label{eqn:kknvf fawoprgj v2}
\end{align}

By the time-homogeneous property of the fluid queue and the memoryless property of the exponential distribution, (\ref{eqn:kknvf fawoprgj v2}) is equal to 
\begin{align}
	&\mathbb P(\bs X(\tau_m^X) =( y_{\ell_{m}+1(j_m\in\calS_-)},j_m), \tau_{m}^X\leq E^\lambda 
		\mid \bs X(\tau_{m-1}) = (y_{\ell_{m-1}+1(j_{m-1}\in\calS_-)}, j_{m-1}), \nonumber
	\\&\tau_{m-1}^X\leq E^\lambda ).\label{eqn: lim 12}
\end{align}
% \begin{align}
% 	&\mathbb P(\bs X(\tau_1^X) = (y_{\ell_{m-1}+1}, j_m), \tau_{1}^X\leq E^\lambda 
%             	 \mid \bs X(0) = (x_0, j_{m-1})) \nonumber
% 	%  \\&=\mathbb P(\bs X(\tau_m^X) = (y_{\ell_{m-1}+1}, j_m), \tau_{m}^X\leq E^\lambda 
%     %         	 \mid \bs X(\tau_{m-1}^X) = (x_0, j_{m-1}))\nonumber 
% 	 \\&=\mathbb P(\bs X(\tau_m^X) = (y_{\ell_{m-1}+1}, j_m), \tau_{m}^X\leq E^\lambda 
%             	 \mid \bs X(\tau_{m-1}^X) = (x_0, j_{m-1}), \nonumber 
% 	\tau_{m-1}^X\leq E^{\lambda}).
% \end{align}
% Similarly, 
% \begin{align}
% 	&\mathbb P(\bs X(\tau_1^X) = (y_{\ell_{m-1}}, j_m), \tau_{1}^X\leq E^\lambda 
%             	 \mid \bs X(0) = (x_0, j_{m-1})) \nonumber
% 	 \\&=\mathbb P(\bs X(\tau_m^X) = (y_{\ell_{m-1}}, j_m), \tau_{m}^X\leq E^\lambda 
%             	 \mid \bs X(\tau_{m-1}^X) = (x_0, j_{m-1}), \tau_{m-1}^X\leq E^\lambda).
% \end{align}

Thus, returning to (\ref{eqn: 161222}) and taking the limit as \(p\to\infty\),  
\begin{align}
	&\lim_{p\to\infty}\sum_{\substack{j_2,\dots,j_{n-1}\in\mathcal S \\ (\ell_2,\dots,\ell_{n-1}) \in\mathcal P^{n-1}_{\ell_1,\ell}}}\prod_{m=2}^{n}\mathbb P(\Ydp(1) = (\ell_m, j_m), \tau_{1}^{(p)}\leq E^\lambda \nonumber
            	 \mid \bs Y^{(p)}(0) = (\ell_{m-1},\bs\alpha, j_{m-1})) \nonumber 
	%
	\\ &=\sum_{\substack{j_2,\dots,j_{n-1}\in\mathcal S \\ (\ell_2,\dots,\ell_{n-1}) \in\mathcal P^{n-1}_{\ell_1,\ell}}}\prod_{m=2}^{n}\lim_{p\to\infty} \mathbb P(\Ydp(1) = (\ell_m, j_m), \tau_{1}^{(p)}\leq E^\lambda 
            	 \mid \bs Y^{(p)}(0) = (\ell_{m-1}, \bs\alpha,
	 	 j_{m-1}) ),
	 \label{eqn: 161222b}
\end{align}
where we may swap the limit and the sums as they are finite, and we can swap the limit and the product since all the limits exist and the product is finite. Substituting the limits (\ref{eqn: lim 12}) into (\ref{eqn: 161222b}) gives 
\begin{align}
	&\sum_{\substack{j_2,\dots,j_{n-1}\in\mathcal S \\ (\ell_2,\dots,\ell_{n-1}) \in\mathcal P^{n-1}_{\ell_1,\ell}}} \prod_{m=2}^{n}\mathbb P(\bs X(\tau_m^X) = (y_{\ell_{m}+1(j_{m}\in\mathcal S_-)}, j_m), \tau_{m}^X\leq E^\lambda\mid \nonumber
            	\\&\qquad\qquad  \bs X(\tau_{m-1}^X)=(y_{\ell_{m-1}+1(j_{m-1}\in\mathcal S_-)},j_{m-1}),\tau_{m-1}^X\leq E^\lambda),\nonumber
		%
		\\&= \mathbb P(\bs X(\tau_n^X) = (y_{\ell+1(j_{n}\in\mathcal S_-)}, 
		j_n), \tau_{n}^X\leq E^\lambda \mid \bs X(0)=(y_{\ell_{1}+1(j_{1}\in\mathcal S_-)},
		j_{1}), 
		\tau_1^X\leq E^\lambda),
\end{align}
by the strong Markov property of the fluid queue and the Law of total probability.

@@

\subsection{Between the \(n\)th and \(n+1\)th orbit restart epochs}\label{sec: between n and np1}
In the last section we proved a convergence of the QBD-RAP to the fluid queue \emph{at} the \(n\)th orbit restart epoch. However, we ultimately want to make a convergence statement about the QBD-RAP scheme at any time. The next step is therefore to show a convergence of the QBD-RAP to the fluid queue between the \(n\)th and \(n+1\)th orbit restart epoch, after which we sum over \(n\) to prove a convergence result independent of the number of orbit restart epochs.

Let \(\mathcal T_n^{(p)} = (\tau_{n}^{(p)},\tau_{n+1}^{(p)}]\) and \(\mathcal T_n^X=(\tau_n^X,\tau_{n+1}^X]\). Consider the Laplace transform 
\begin{align}
	&\int_{t=0}^\infty e^{-\lambda t}\int_{x\in\calD_{\ell,j}}\mathbb P({\bs Y}^{(p)}(t) = (\ell, \wrt x, j), t\in\mathcal T_n^{(p)} \mid 
	\bs Y^{(p)}(0)=\bs y_0^{(p)})\psi(x)\wrt t, \label{eqn: aaabbababbaa}
	% \nonumber&\int_{t=0}^\infty e^{-\lambda t}\int_{x\in\calD_\ell}\mathbb P(L^{(p)}(t) = \ell, \widetilde X^{(p)}(t)\in\wrt x, \phi^{(p)}(t) = j, \tau_{n}^{(p)}\leq t<\tau_{n+1}^{(p)} \mid L^{(p)}(0)=\ell_0, 
	% 	\\&\qquad \bs A^{(p)}(0)=\bs a_{\ell_0,i}^{(p)}(x_0), \phi^{(p)}(0)=i)\psi(x)\wrt t.
\end{align}
where \(\psi:\mathbb R\to \mathbb R\) is a bounded function.

Partitioning (\ref{eqn: aaabbababbaa}) on the time of the \(n\)th orbit restart epoch and the phase and level at this time gives
\begin{align}
	&\int_{t=0}^\infty e^{-\lambda t} 
	\int_{x\in\calD_{\ell,j}}
	\int_{u_n=0}^t\sum_{j_n\in\mathcal S} \mathbb P({\bs Y}^{(p)}(t) = (\ell,\wrt x,j), 
	t \in(u_n, \tau_{n+1}^{(p)}] \mid\Ydp(n) = (\ell,j_n), \nonumber 
	\\&\quad \tau_{n}^{(p)}= u_n)\psi(x) \mathbb P(\Ydp(n) = (\ell, j_n), \tau_{n}^{(p)}\in \wrt u_n 
	 \mid \bs Y^{(p)}(0)=\bs y_0^{(p)}) 
	  \wrt t \nonumber 
	 %
	 \\&= \sum_{j_n\in\mathcal S}
	\int_{x\in\calD_{\ell,j}} \int_{t=0}^\infty e^{-\lambda t} \mathbb P({\bs Y}^{(p)}(t) = (\ell,\wrt x, j), 
	t\in\mathcal T_{0}^{(p)} \mid\nonumber 
	  \bs Y(0) = (\ell,\bs\alpha,j_n))\wrt t \psi(x)  
	  \\&\quad{} \mathbb P(\Ydp(n) = (\ell,j_n), \tau_{n}^{(p)}\leq E^\lambda 
	 \mid \bs Y^{(p)}(0)=\bs y_0^{(p)}) \label{eqn: l whkrqvlkjbrd}
\end{align}
by the time homogenous property of the QBD-RAP, the memoryless property of the exponential distribution, and the convolution theorem of Laplace transforms. The swap of integrals and sums is justified by the Fubini-Tonelli Theorem. We recognise the probability 
\begin{align}
	\mathbb P(\Ydp(n) = (\ell, j_n), \tau_{n}^{(p)}\leq E^\lambda 
	 \mid \bs Y^{(p)}(0)=\bs y_0^{(p)}) \label{eqn: Kkk nj aa w}
\end{align}
as that appearing in Lemma \ref{lem: kKKJJJF}, hence (\ref{eqn: Kkk nj aa w}) converges to 
\begin{align}
	\mathbb P(\bs X(\tau_n^X) = (y_{\ell+1(j_{n}\in\mathcal S_-)}, 
		j_n), \tau_{n}^X\leq E^\lambda
		\mid \bs X(0)=(x_0, i)) \label{eqn: ashverkjbvjhkhdsknacva}
\end{align}
as \(p\to\infty\).

Now consider the expression 
\begin{align}
	&\int_{x\in\calD_{\ell,j}} \int_{t=0}^\infty e^{-\lambda t} \mathbb P({\bs Y}^{(p)}(t) = (\ell,\wrt x, j),  
	t\in\mathcal T_0^{(p)} \mid \bs Y(0) = (\ell,\bs\alpha, j_n)
	 	 )\wrt t  \psi(x)  \label{eqn: vajkl;vJK:GSKJ}
\end{align}
which appears as part of (\ref{eqn: l whkrqvlkjbrd}). We can rewrite (\ref{eqn: vajkl;vJK:GSKJ}) as  
\begin{align}
	 &\int_{x\in\calD_{\ell,j}} \int_{t=0}^\infty e^{-\lambda t} \mathbb P({\bs Y}^{(p)}(t) = (\ell,\wrt x,j), 
	t\in\mathcal T_0^{(p)}\mid \Ydp(0) = (\ell,j_n))\wrt t \psi(x) \nonumber 
	 \\&= \int_{x\in\calD_{\ell,j}} \widehat f^{\ell,(p)} (\lambda)(x,j;y_{\ell+1(j_n\in\mathcal S_-)},j_n) \psi(x)\wrt x \label{eqn: Jk jJ KK}
\end{align}
Applying Theorem~\ref{thm: a thm!}, then (\ref{eqn: Jk jJ KK}) converges to 
\begin{align}
	&\int_{x\in\calD_{\ell,j}} \widehat \mu^{\ell} (\lambda)(x,j;y_{\ell+1(j_n\in\mathcal S_-)},j_n) \psi(x)\wrt x \nonumber 
	\\&= \int_{x\in\calD_{\ell,j}} \int_{t=0}^\infty e^{-\lambda t}\mathbb P(\bs X(t)\in(\wrt x, j), t\in\mathcal T_0^X \mid \bs X(0) = (y_{\ell+1(j_n\in\mathcal S_-)}, j_n) ) \psi(x). \label{eqn: lkHAHJFHKJ J J H}
\end{align}
Since the fluid queue is time-homogeneous and \(E^\lambda\) memoryless, then (\ref{eqn: lkHAHJFHKJ J J H}) is equal to 
\begin{align}
	&\int_{x\in\calD_{\ell,j}} \int_{t=0}^\infty e^{-\lambda t} \mathbb P(\bs X(t)\in(\wrt x,j), t\in\mathcal T_n^{X} \mid  
	\bs X(\tau_n^X) = (y_{\ell+1(j_n\in\mathcal S_-)},j_n), \tau_n^X\leq E^\lambda ) \psi(x).  \label{eqn: lkHAHJFHKJ J J 22}
\end{align}
Therefore, we have shown (\ref{eqn: vajkl;vJK:GSKJ}) converges to (\ref{eqn: lkHAHJFHKJ J J 22}) as \(p\to\infty\).
